Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-04 vesicle_code/docs/permeableVes/main.tex
fixed fig 7
yny

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%
In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
investigate the effects of native water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. 
%
Coupling the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

To understand the effects of water permeability on cells that repeatedly
go through micro-capillary vessels or sub-micron slits, we construct a
contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
simulate a vesicle passing through the contracting geometry six times.
In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
deflates each time it passes through the contraction followed by a
gradual inflation (over seconds). The total area loss over the history
of the vesicle is almost 50\%. In
Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
a function of the vesicle's center of mass. As the vesicle passes
through the contraction, it first accelerates until it reaches the neck
where it abruptly decelerates to go through the contraction. The
variation of the reduced area and velocity with respect to time are also
shown in Figure~\ref{fig:contractingComposite2}.
\begin{figure}[hbp]
  \centering
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
  six periods of the contracting geometry. (b) The reduced area with
  the marks representing shapes in (a). (c) The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.\todo[inline]{Make the
  time steps equispaced and the values of $x$ non-uniform. Reverse their
  orders between to and bottom.}}
\end{figure}

>>>>

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for water molecules. Under an external load 
 the water influx/efflux is often assumed  negligible in the absence of osmolarity, provided 
that the lipid bilayer membrane remains intact (no poration or rupture),. 
%
In this work we use boundary integral simulations to investigate the effects
of native water permeability on the vesicle hydrodynamics due to a mechanical load,  such as the viscous stress
from an external flow deforming a vesicle in free space or pushing the vesicle through a confinement. Coupling the 
membrane permeability with membrane elastic stress and tension in the framework of Helfrich free energy, we 
illustrate that, in the absence of an osmotic stress gradient, a giant unilamellar vesicle may be affected by water 
influx/efflux over a sufficiently long time or under a strong confinement. Our simulation results quantify the conditions 
for water permeation to be negligible in terms of the time scales, flow strength and confinement. These results shed 
light on how microfluidic confinement can be utilized to estimate membrane permeability.
%
%Lipid bilayer membranes have a native (albeit small) permeability for
%water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
%often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%%
%In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
%investigate the effects of native water permeability on the hydrodynamics of
%a vesicle under various flows and confinement configurations. 
%%
%Coupling the membrane permeability with membrane elastic stress, tension, and
%mechanical stress in the framework of Helfrich free energy, we
%illustrate that, in the absence of an osmotic stress gradient, a giant
%unilamellar vesicle may be significantly affected by water
%influx/efflux over a sufficiently long time or under a strong
%confinement. Our simulation results quantify the conditions for water
%permeation to be negligible in terms of the time scales, flow strength
%of an external flow, and degree of confinement. These results shed
%light on how microfluidic confinement can be utilized to estimate
%membrane permeability.
%%
%%osmotic stress gradient 
%%We describe a mathematical model for a semipermeable vesicle and derive
%%  a boundary integral equation formulation for simulating its
%%  hydrodynamics.  
%%
%%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

To understand the effects of water permeability on cells that repeatedly
go through micro-capillary vessels or sub-micron slits, we construct a
contracting geometry (see Figures~\ref{fig:contractingComposite2}) to
simulate a vesicle passing through the contracting geometry six times.
In Figure~\ref{fig:contractingComposite2}b, we show that the vesicle
deflates each time it passes through the contraction followed by a
gradual inflation (over seconds). The total area loss over the history
of the vesicle is almost 50\%. In
Figure~\ref{fig:contractingComposite}c, we show the vesicle velocity as
a function of the vesicle's center of mass. As the vesicle passes
through the contraction, it first accelerates until it reaches the neck
where it abruptly decelerates to go through the contraction. The
variation of the reduced area and velocity with respect to time are also
shown in Figure~\ref{fig:contractingComposite2}.
\begin{figure}[hbp]
  \centering
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
  six periods of the contracting geometry. (b) The reduced area with
  the marks representing shapes in (a). (c) The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure}
